Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-11 mtjournal.tex
clean up tables to save some space
added table with per-seg HTER correlations

In table~\ref{tab:facorr:combinations}, we compare among several other
members of the DPM family. 
 \begin{table}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$r$} \\
    \hline
    $F[1g,2g,dl,lh]$      &  0.237 \\
    $\mu_{PR}[1g,2g,dl,lh]$ &  0.217 \\
    \\
    $F[1g,2g]$            & 0.227 \\
    $F[1g,dl,dlh]$        & 0.227 \\
    \\
    $F[dl,lh]$            &  0.226 \\
    $\mu_{PR}[dl,lh]$      &  0.208 \\
    \hline
  \end{tabular*}
  \caption{Comparing combination methods $F[\cdot]$ and
    $\mu_{PR}[\cdot]$, and comparing the $1g,2g,dl,lh$ decomposition
    with the $dl,lh$ decomposition and other decompositions.}
  \label{tab:facorr:combinations}
\end{table}
Here, we find that combining the decompositions naively in $F[\cdot]$
(before computing precision and recall) has a better $r$ than the
harmonic mean of precision and recall subscores in $\mu_{PR}[\cdot]$.
We also see that we can combine the benefits of string-local $n$-grams
($F[1g,2g]$) with the benefits of dependency information ($F[dl,lh]$)
for a further improved correlation with human judgment, with the best
correlation in $F[1g,2g,dl,lh]$. Including progressively larger chunks
of the dependency graph (as in $F[1g,dl,dlh]$, which is inspired by
the BLEU$_k$ idea of progressively larger $n$-grams) does not seem to
be an improvement over $F[dl,lh]$.

@@

To explore the effect of extracting parse feature-counts from a forest
instead of a single tree, we present in
table~\ref{tab:facorr:multiparse} several variants, with $n=1$ and
with $n=50$.  
 \begin{table}
  \begin{tabular*}{2.5in}{lrr}
    \hline
    metric  & \multicolumn{1}{c}{$n$} &  \multicolumn{1}{c}{$r$} \\
    \hline
    $F[1g,2g,dl,lh]$      & 50 &  0.239 \\
    $F[1g,2g,dl,lh]$      &  1 &  0.237 \\
    \\
    $F[1g,dl,lh]$            &  50 & 0.237 \\
    $F[1g, dl,lh]$            &  1 & 0.234 \\
    \\
    $F[dl,lh]$            &  50 & 0.234 \\
    $F[dl,lh]$            &  1 & 0.226 \\
    \hline
  \end{tabular*}
  \caption{Comparing $n=1$ to $n=50$ for several variants of the DPM measure.}
  \label{tab:facorr:multiparse}
\end{table}
For the $n=50$ cases, we set $\gamma=0$ to assign
uniform probabilities to the parse forest, to compare as closely as
possible to \inlinecite{owczarzak07labelleddepseval}, which includes a
\textbf{d\_var\_50} measure with 50-best parses, with ranks but no
weights.  While not all of these differences are significant, the
trend is universally that the correlation $r$ improves as the number
of parses ($n$) is increased.
Tuning experiments find that increasing $\gamma$ to 0.25 can increase
the $r$ reported here for $F[1g,2g,dl,lh]$ marginally (but insignificantly).

@@

The GALE 2.5 translation corpus is made up of system translations into
English from three sites.
% MO added:
The three sites all use system combination to integrate results from
multiple systems, some of which are phrase-based and some which may
use syntax on either the source or target side. No system provided
system-generated parses.
%
The corpus being translated comes from
Arabic and Chinese in four genres: \texttt{bc} (broadcast
conversation), \texttt{bn} (broadcast news), \texttt{nw} (newswire),
and \texttt{wb} (web text), with corpus sizes shown in
table~\ref{tab:galestats}.
\begin{table}
  \begin{tabular}{r|rr|rr|rr}
     & \multicolumn{2}{c|}{Arabic} & \multicolumn{2}{c|}{Chinese}
     & \multicolumn{2}{c}{Total}\\
     & doc & sent & doc & sent & doc   & sent\\
     \hline
     \texttt{bc}    & 59  & 750 & 56 & 1061 & 115 & 1811\\
     \texttt{bn}    & 63  & 666 & 63 & 620  & 126 & 1286\\
     \texttt{nw}    & 68  & 494 & 70 & 440  & 138 & 934 \\
     \texttt{wb}    & 69  & 683 & 68 & 588  & 137 & 1271\\
     \hline
     Total & 259 & 2593& 257& 2709 & 516 & 5302\\
  \end{tabular}
  \caption{Corpus statistics for the GALE 2.5 translation
    corpus.}
  \label{tab:galestats}
\end{table}
The corpus includes one English reference translation $r_i$
\cite{gale08phase2_5references} for each sentence $i$ and a system
translation $t_{i,z}$ for each of the three systems $z$. Additionally,
each of the system translations of each segment $i$ has a
corresponding human-targeted reference aligned at the sentence level,
so we have available the HTER score of each segment
$s_{\textrm{HTER}}(t_{i,z})$ at both the sentence and document level.

@@

>>>>

In table~\ref{tab:facorr:combinations}, we compare among several other
members of the DPM family. 
 \begin{table}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$r$} \\
    \hline
    $F[1g,2g,dl,lh]$      &  0.237 \\
    $\mu_{PR}[1g,2g,dl,lh]$ &  0.217 \\
    \rlcline{1-1} \rlcline{2-2}
    $F[1g,2g]$            & 0.227 \\
    $F[1g,dl,dlh]$        & 0.227 \\
    \rlcline{1-1} \rlcline{2-2}
    $F[dl,lh]$            &  0.226 \\
    $\mu_{PR}[dl,lh]$      &  0.208 \\
    \hline
  \end{tabular*}
  \caption{Comparing combination methods $F[\cdot]$ and
    $\mu_{PR}[\cdot]$, and comparing the $1g,2g,dl,lh$ decomposition
    with the $dl,lh$ decomposition and other decompositions.}
  \label{tab:facorr:combinations}
\end{table}
Here, we find that combining the decompositions naively in $F[\cdot]$
(before computing precision and recall) has a better $r$ than the
harmonic mean of precision and recall subscores in $\mu_{PR}[\cdot]$.
We also see that we can combine the benefits of string-local $n$-grams
($F[1g,2g]$) with the benefits of dependency information ($F[dl,lh]$)
for a further improved correlation with human judgment, with the best
correlation in $F[1g,2g,dl,lh]$. Including progressively larger chunks
of the dependency graph (as in $F[1g,dl,dlh]$, which is inspired by
the BLEU$_k$ idea of progressively larger $n$-grams) does not seem to
be an improvement over $F[dl,lh]$.

@@

To explore the effect of extracting parse feature-counts from a forest
instead of a single tree, we present in
table~\ref{tab:facorr:multiparse} several variants, with $n=1$ and
with $n=50$.  
 \begin{table}
  \begin{tabular*}{2.5in}{lrr}
    \hline
    metric  & \multicolumn{1}{c}{$n$} &  \multicolumn{1}{c}{$r$} \\
    \hline
    $F[1g,2g,dl,lh]$      & 50 &  0.239 \\
    $F[1g,2g,dl,lh]$      &  1 &  0.237 \\
    \rlcline{1-2}\rlcline{3-3}
    $F[1g,dl,lh]$            &  50 & 0.237 \\
    $F[1g, dl,lh]$            &  1 & 0.234 \\
    \rlcline{1-2}\rlcline{3-3}
    $F[dl,lh]$            &  50 & 0.234 \\
    $F[dl,lh]$            &  1 & 0.226 \\
    \hline
  \end{tabular*}
  \caption{Comparing $n=1$ to $n=50$ for several variants of the DPM measure.}
  \label{tab:facorr:multiparse}
\end{table}
For the $n=50$ cases, we set $\gamma=0$ to assign
uniform probabilities to the parse forest, to compare as closely as
possible to \inlinecite{owczarzak07labelleddepseval}, which includes a
\textbf{d\_var\_50} measure with 50-best parses, with ranks but no
weights.  While not all of these differences are significant, the
trend is universally that the correlation $r$ improves as the number
of parses ($n$) is increased.
Tuning experiments find that increasing $\gamma$ to 0.25 can increase
the $r$ reported here for $F[1g,2g,dl,lh]$ marginally (but insignificantly).

@@

The GALE 2.5 translation corpus is made up of system translations into
English from three sites.
% MO added:
The three sites all use system combination to integrate results from
multiple systems, some of which are phrase-based and some which may
use syntax on either the source or target side. No system provided
system-generated parses.
%
The corpus being translated comes from
Arabic and Chinese in four genres: \texttt{bc} (broadcast
conversation), \texttt{bn} (broadcast news), \texttt{nw} (newswire),
and \texttt{wb} (web text), with corpus sizes shown in
table~\ref{tab:galestats}.
\begin{table}
  \begin{tabular}{r|rr|rr|rr}
    \hline
     & \multicolumn{2}{c|}{Arabic} & \multicolumn{2}{c|}{Chinese}
     & \multicolumn{2}{c}{Total}\\
     & doc & sent & doc & sent & doc   & sent\\
     \hline
     \texttt{bc}    & 59  & 750 & 56 & 1061 & 115 & 1811\\
     \texttt{bn}    & 63  & 666 & 63 & 620  & 126 & 1286\\
     \texttt{nw}    & 68  & 494 & 70 & 440  & 138 & 934 \\
     \texttt{wb}    & 69  & 683 & 68 & 588  & 137 & 1271\\
     \hline
     Total & 259 & 2593& 257& 2709 & 516 & 5302\\
     \hline
  \end{tabular}
  \caption{Corpus statistics for the GALE 2.5 translation
    corpus.}
  \label{tab:galestats}
\end{table}
The corpus includes one English reference translation $r_i$
\cite{gale08phase2_5references} for each sentence $i$ and a system
translation $t_{i,z}$ for each of the three systems $z$. Additionally,
each of the system translations of each segment $i$ has a
corresponding human-targeted reference aligned at the sentence level,
so we have available the HTER score of each segment
$s_{\textrm{HTER}}(t_{i,z})$ at both the sentence and document level.

@@

In table~\ref{tab:hterpersent}, we see a similar story.
\begin{table}
  \begin{tabular}{r|rrrr|rr|r}
    \hline
    $r$ vs. $\bar{\mu}$HTER & \multicolumn{1}{c}{\texttt{bc}}
    & \multicolumn{1}{c}{\texttt{bn}} &
    \multicolumn{1}{c}{\texttt{nw}} & \multicolumn{1}{c}{\texttt{wb}}
    & \multicolumn{1}{|c}{all Arabic} & \multicolumn{1}{c|}{all Chinese}
    & \multicolumn{1}{c}{all} \\
    \hline
    $\bar{\mu}$TER
    &  \textbf{0.44} &  \textbf{0.29} &  \textbf{0.33}&  0.25
    & \textbf{0.44} & 0.25  &  \textbf{0.36}\\
    $\bar{\mu}$BLEU
    & -0.31 & -0.24  & -0.29 &  -0.25
    & -0.31  &  -0.24  & -0.28 \\
    $\bar{\mu}$EDPM
    & \textbf{-0.46} & \textbf{-0.31} & \textbf{-0.34} &
    \textbf{-0.30}
    & \textbf{-0.44} & \textbf{-0.30} & \textbf{-0.37} \\
    \hline
  \end{tabular}
  \caption{Per-sentence, length-weighted correlations of
    $\bar{\mu}$EDPM and others to $\bar{\mu}$HTER, by genre and by
    source language. Bold numbers are within 95\% significance of the
    best per column.}
  \label{tab:hterpersent}
\end{table}
